---
title: "Homework 1"
author: "Nana Kwaku Amoako"
date: "2024-01-20"
output: word_document
---

```{r setup, message = FALSE}
library(readr)
H1N1_Flu_Vaccines <- read_delim("/Users/nanaamoako/Library/CloudStorage/OneDrive-AshesiUniversity/Ashesi/Year 2/January 2024 Semester/Statistics/Week 2/Assignments/H1N1_Flu_Vaccines.txt")
library(MASS)
?anorexia
View(anorexia)

```

### Question 1
```{r}
## Summary of Results:
## -------------------
## The pie chart visually represents the distribution of respondent's levels of concern about the H1N1 flu. The chart shows that 30% of respondents reported being not concerned, 40% were somewhat concerned, and another 30% expressed very concerned. The legend provides additional clarity by displaying the exact percentage values for each category. This representation offers a quick and clear overview of the varying levels of concern within the surveyed population.


```
# Create a table
t = table(H1N1_Flu_Vaccines$h1n1_concern);t

# View the proportion of the total in each category 
prop = prop.table(t);prop

# View the percentage of the total in each category 
percent = prop.table(t) * 100; percent

# Round to one decimal place
pf = round(percent, 1) ;pf

# Label the percentages
lbl = paste(c("Not at all concerned ", "Not very concerned ", "Somewhat concerned ", "Very concerned  "),pf,"%",sep="");lbl

# Create a pie chart
pie(t, label = lbl)

# Add a title
title(main = 'Respondents\' Level of Concern about H1N1 Flu')

